Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-08-16 xrb/paper.tex
add the time series plot
add a table of simulations:

We specify the rotation period, $P_\mathrm{rot}$, which is related to
the angular rotation rate as $\Omega = 2\pi / P_\mathrm{rot}$.  Our
default rotation period is $0.0005~\mathrm{s}$ (2000 times per
second).  This is quite fast, but picked to make the Rossby length
small enough to fit in the spatial scales we can model.  With this
rotation rate, the Rossby length is
\begin{equation}
L_R = \frac{\sqrt{g H_0}}{\Omega} \sim 3\times 10^4~\mathrm{cm}
\end{equation}
\MarginPar{we should make the width of the hot region closer to the
  Rossby length} using a scale height $H_0 = 10^3~\mathrm{cm}$.  This
is less than half our domain width.

@@

@@

@@

>>>>

We specify the rotation period, $P_\mathrm{rot}$, which is related to
the angular rotation rate as $\Omega = 2\pi / P_\mathrm{rot}$.  Our
default rotation period is $0.0005~\mathrm{s}$ (2000 times per
second).  This is quite fast, but picked to make the Rossby length
small enough to fit in the spatial scales we can model.  With this
rotation rate, the Rossby length is
\begin{equation}
L_R = \frac{\sqrt{g H_0}}{\Omega} \sim 3\times 10^4~\mathrm{cm}
\end{equation}
\MarginPar{we should make the width of the hot region closer to the
  Rossby length} using a scale height $H_0 = 10^3~\mathrm{cm}$.  This
is less than half our domain width.  Table~\ref{table:sim_names} lists
the simulations run and their parameters.

@@

\begin{deluxetable}{lccccc}
\tablecaption{\label{table:sim_names} Simulaiton parameters.}
\tablehead{\colhead{name} & \colhead{reaction boost} & \colhead{conductivity boost} & \colhead{fine grid resolution} & \colhead{rotation rate}  & \colhead{network}}
\startdata
10/10 & 10 & 10 & 10~cm & 2000~Hz & {\tt aprox13} \\
10/10 slow & 10 & 10 & 10~cm & 1000~Hz & {\tt aprox13} \\
10/10 lores & 10 & 10 & 20~cm & 2000~Hz & {\tt aprox13} \\
5/5 & 5 & 5 & 10~cm & 2000~Hz & {\tt aprox13} \\
10/10 iso7 & 10 & 10 & 10~cm & 2000~Hz & {\tt iso7} \\
\enddata
\end{deluxetable}

@@

Figure~\ref{fig:time_series} shows the time

@@

\begin{figure}[h]
\centering
\epsscale{0.95}
\plotone{time_series}
\caption{\label{fig:time_series} Time series of the mean molecular weight of the 
flame for our standard 10/10 flame.}
\end{figure}
